Model LF

### 2023-03-16 paper version Hamid new test.Rmd
commit

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
   alpha = TIMESERIES(c(alpha),   
                       START=c(2005,2),FREQ=4),
  wage_ben_gap = TIMESERIES(c(wage_ben_gap),   
                       START=c(2005,2),FREQ=4)
  )
```

@@

wage_gap1_bs1-wage_ben_gap
wage_gap1_01-wage_ben_gap

plot(wage_gap1_bs1-wage_ben_gap, col="blue"); lines(wage_gap1_01-wage_ben_gap)

>>>>

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
   alpha = TIMESERIES(c(alpha),   
                       START=c(2005,2),FREQ=4),
  wage_ben_gap = TIMESERIES(c(wage_ben_gap),   
                       START=c(2005,2),FREQ=4)
  )
```

@@
